---
title: "IMDB Analysis"
author: "Jin Huang"
date: "April 9, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(dplyr)
library(plotly)
```

## R Markdown
This is an R Markdown presentation exploring IMDB 5000 Movie Dataset,  <https://www.kaggle.com/deepmatrix/imdb-5000-movie-dataset>.

Espeically we would like to check the relationship between actors' facebook (FB) likes with IMDB score.  

```{r echo = FALSE}
# Read data from a local csv file downloaded from the website above
movies <- read.csv('movie_metadata.csv', header=TRUE, stringsAsFactors = FALSE)

# Remove any rows with NA
movies <- movies[complete.cases(movies),]

# Remove the outliers, which are defined as outside of 2 times of standard deviation
movies_without_FBols <- movies %>% filter(!(abs(actor_1_facebook_likes - median(actor_1_facebook_likes)) >  2 * sd(actor_1_facebook_likes)))
```

## IMDB score vs FB likes of both actor 1 and 2
```{r echo = FALSE}
plot_ly(data = movies_without_FBols, x = ~actor_1_facebook_likes, y = ~actor_2_facebook_likes, z = ~imdb_score,
        type = "scatter3d", color = ~imdb_score)
```

## IMDB score vs FB likes of the entire cast
```{r echo = FALSE}
plot_ly(data = movies_without_FBols, x = ~cast_total_facebook_likes, y = ~imdb_score, type = "scatter", color = ~imdb_score)
```

## Conculsions
- In general, the higher FB likes, the higher score in IMDB.  If you would like to pick a movie without knowing IMDB scores, it is safe to find one with cast members who are very popular on FB.  

- However, many good movies with high scores also show low FB likes.  So don't just follow the FB trends.